XOR-Some Prolific Pilot 2

### 2021-08-19 analysis/xor-some-prolific-pilot2.Rmd
add final items
first stab at simr based power analysis

d_critical_long %>% 
  mutate(title = paste(title, exp_condition, sep = "_"),
         block = ifelse(block == "xor" | block == "some", "target", block)) %>%
  left_join(., d_critical_long_grandMeans, by = c("main_type", "block")) %>% filter(block == class_condition | block == "target") -> d_long_place_holder

left_join(d_long_place_holder, d_critical_long_expectedCats, by = c("main_type", "block", "title")) %>% 
  mutate(expected_block = ifelse(block != "target", prior_class * 100, NA),
         block = factor(block, levels = c("relevance", "competence", "prior"))) %>%
  ggplot(., aes(x = block, y = response, color = block)) +
  geom_point(alpha = 0.7, position = position_jitter(width = 0.1)) +
  geom_hline(aes(yintercept = mean_resp), alpha = 0.7) +
  geom_point(aes(y = mean_resp), color = "black", shape = 2) +
  geom_point(aes(y = mean_resp_block, fill = block), color = "black") +
  geom_point(aes(y = expected_block), color="red", size = 2.5) +
  ylab("Raw responses to respective questions") +
  facet_wrap(main_type~title, ncol = 4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("By-item by-question raw ratings\nBlack dots indicate by-block means within-item, lines and triangles indicate grand by-block means\nRed dots indicate expected rating")
```
For the following items, participants seem  to *disagree* in their judgments for all of the predictors: Emails from a broken laptop, Gift unwrapping, Martha's cookies, Suzie's fruits, Brad's clothes, Crime, maybe more..

@@

@@

>>>>

d_critical_long %>% 
  mutate(title = paste(title, exp_condition, sep = "_"),
         block = ifelse(block == "xor" | block == "some", "target", block)) %>%
  left_join(., d_critical_long_grandMeans, by = c("main_type", "block")) %>% 
  filter(block == class_condition | ((block == "target") & (class_condition == "relevance"))) -> d_long_place_holder

left_join(d_long_place_holder, d_critical_long_expectedCats, by = c("main_type", "block", "title")) %>% 
  mutate(expected_block = ifelse(block != "target", prior_class * 100, NA),
         block = factor(block, levels = c("relevance", "competence", "prior", "target"))) -> d_long_plot_full

# save preprocessed df for plotting for comparison with third pilot
# d_long_plot_full %>% write_csv("../data/pilots/pilot2_byItem_plotting.csv")

d_long_plot_full %>%
  ggplot(., aes(x = block, y = response, color = block)) +
  geom_point(alpha = 0.7, position = position_jitter(width = 0.1)) +
  geom_hline(aes(yintercept = mean_resp), alpha = 0.7) +
  geom_point(aes(y = mean_resp), color = "black", shape = 2) +
  geom_point(aes(y = mean_resp_block, fill = block), color = "black") +
  geom_point(aes(y = expected_block), color="red", size = 2.5, na.rm = T) +
  ylab("Raw responses to respective questions") +
  facet_wrap(main_type~title, ncol = 4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("By-item by-question raw ratings\nBlack dots indicate by-block means within-item, lines and triangles indicate grand by-block means\nRed dots indicate expected rating")
```
For the following items, participants seem  to *disagree* in their judgments for all of the predictors: Emails from a broken laptop, Gift unwrapping, Martha's cookies, Suzie's fruits, Brad's clothes, Crime, maybe more..

@@

#d_critical_zScored_wide %>%
#  write_csv("../data/pilots/pilot2_critical_zScore_wide_tidy.csv")

@@

Now we explore the original analysis with the by-item means:
